\textbf{Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata} \textbackslash{} Appendix

### 2023-07-10 manuscript_v6/02-methods.qmd
updated files, sent to Overleaf

Briefly, the survey was deployed using random domain intercept technology, a methodology where internet users whose device meta-data indicated their presence in the province of Ontario had a random chance of being redirected to the survey after they had clicked on a registered but commercially inactive web link, or typed in a web address for a site that was dormant but that was temporarily managed by the company that administered the survey (RIWI Corp) [@sargent2022]. Users then decided whether to anonymously participate in the survey, and those that participated were able to exit the survey at any time. After the survey closed, regardless if it was complete or incomplete, access was denied to any further users with the same internet protocol address (IP), effectively allowing each user only one opportunity to participate in the survey. Users who indicated they were under the age of 16 were exited from the survey without creating a record. Finally, the personal identifier information from each user that participated in the survey was automatically scrubbed and replaced by a unique ID.

>>>>

Briefly, the survey was deployed using Random Domain Intercept Technology (RDIT), a methodology for internet surveys developed by the company commissioned to run the survey (RIWI Corp., Toronto, Canada), and that has been used in the area of public health research to examine trends in vaccination rates[@sargent2022], ratings of care quality[@kim2021], and perceptions of vaccine efficacy[@seeman2010]. In the case of the survey used for this study, internet users whose device meta-data indicated their presence in the province of Ontario had a random chance of being redirected to the survey after they had clicked on a registered but commercially inactive web link, or after they had typed in a web address for a site that was dormant but that was temporarily managed by RIWI. Users then decided whether to anonymously participate in the survey, and those that participated were able to exit the survey at any time. After the survey closed, regardless if it was complete or incomplete, access was denied to any further users with the same internet protocol address (IP), effectively allowing each user only one opportunity to participate in the survey. Users who indicated they were under the age of 16 were exited from the survey without creating a record. Finally, the personal identifier information from each user that participated in the survey was automatically scrubbed and replaced by a unique ID.

### 2023-07-10 manuscript_v6/appendix.tex
updated files, sent to Overleaf

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
%start sections and page numbers with A
\usepackage{placeins}
\setcounter{page}{1}
\renewcommand\thesection{A}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\renewcommand{\thepage}{A-\arabic{page}}
\renewcommand{\thetable}{A-\arabic{table}}
\renewcommand\thefigure{\thesection-\arabic{figure}}

@@

\affil[1]{Centre de Recherches Mathématiques, University of Montreal,
Montréal, Canada}
\affil[2]{Department of Social and Preventive Medicine, École de Santé
Publique, University of Montreal, Montréal, Canada}
\affil[3]{Centre de recherche en santé publique, University of Montreal,
Montréal, Canada}
\affil[*]{Corresponding author, \url{bouchra.nasri@umontreal.ca}}

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
%start sections and page numbers with A
\usepackage{placeins}
\setcounter{page}{1}
\renewcommand\thesection{A}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\renewcommand{\thepage}{A-\arabic{page}}
\renewcommand{\thetable}{A-\arabic{table}}
\renewcommand\thefigure{\thesection-\arabic{figure}}

@@

\affil[1]{Centre de Recherches Mathématiques, University of Montreal,
Montréal, Canada}
\affil[2]{Department of Social and Preventive Medicine, École de Santé
Publique, University of Montreal, Montréal, Canada}
\affil[3]{Centre de recherche en santé publique, University of Montreal,
Montréal, Canada}
\affil[*]{Corresponding author,
\href{mailto:bouchra.nasri@umontreal.ca}{bouchra.nasri@umontreal.ca}}

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi
